---
title: "Next Steps?"
format: html
---
### General Info
Description:
This is a document to see what each member has done, so we can see what are our next steps. 

## Nov 4

Note that there is already the highlightr package. Perhaps you can find a way to combine this with the git history using the git2r package?

I'm wondering if you can apply the concepts of highlightr to source code, using the git history as "notes", as described here.

Please use this repository and get started!


## Nov 9

Nicole went to a meeting with Baumer so we can describe our next steps. One thing that Prof. Baumer suggested is to make summary table 

We first looked at blame in the git2r package
```{r}
library(git2r)
blame(path="README.md")

#then we saved it to x
blame(path="README.md") -> x
#then find the class
class(x) # we did this so we it is, and it is git_blame
str(x) #this can show us the histroy of the changes/commits

```

```{r}
commits_amt <- function(file_name) {
  
  ##Keep a history of commits
  # Help you open a repository 
  repo <- git2r::repository(path = file_name ) # https://docs.ropensci.org/git2r/ 

  
  #count the amount of commits 
  num_c <- length(git2r::commits(repo))
  paste("The amount of commits so far is: ", num_c)
  
}
commits_amt(file_name = "README.md")
```



Then we can try to make a summary table of each user who made a commit, and how many times they committed, this would be for each file.

This summary could apply to any file in the repository, or even across the entire repo, to get a complete count of contributions and edited files by user.

## Next Steps

Generate a summary table showing each user who contributed, the number of commits they made, and the specific files they edited.

Test it out with other Repos?

Extra notes:
Professor Baumer said that GitHub’s  doesn’t really do a great job helping you understand of who’s responsible in your repository maybe we can take this into consideration of what we can do with chchchanges


## Nov 19
I think I'm gonna make a function that will generalize the file blame paht to a lot of filees instead of just README.md,
-Ananda _> where the lines were made on
- Debora _> trying to find how to find the amount of commits per file, previous functions seems to only find the number of commits for the whole repository
-Nicole _> trying to combine this all into summary table function,